Supplemental Figures: Aligning marine species range data to better serve science and conservation

### 2016-09-25 ms_3_res_disc_concl.Rmd
cleaning up and preparing to make public for submit

![](figures/Fig_1.png)

@@

![](figures/Fig_2.png)

> __Fig 2. Comparison of alignment between AquaMaps and IUCN range data.__ (A) Distribution alignment (overlap of smaller range within larger) versus area ratio (the ratio of smaller range area to the larger range area) for `r format(n_spp_both, big.mark = ',')` species included in both IUCN and AquaMaps datasets.  The upper right quadrant (quadrant 1) comprises species whose maps largely agree in both spatial distribution and the extent of described ranges (n = `r n_q1`; `r round(n_q1/nrow(spp_list_quads) * 100, 1)` %).
The upper left quadrant (quadrant 2) comprises species whose maps agree well in distribution, but disagree in area
(n = `r n_q2`; `r round(n_q2/nrow(spp_list_quads) * 100, 1)` %).
The lower right quadrant (quadrant 3) includes species for which the paired maps generally agree in range area, but disagree on where those ranges occur
(n = `r n_q3`; `r round(n_q3/nrow(spp_list_quads) * 100, 1)` %).
The lower left quadrant (quadrant 4) indicates species for which the map pairs agree poorly in both area and distribution
(n = `r n_q4`; `r round(n_q4/nrow(spp_list_quads) * 100, 1)` %).
(B) Alignment quadrant breakdown of species by taxonomic group.

@@

![](figures/Fig_3.png)

@@

![](figures/Fig_4.png)

@@

![](figures/Fig_5.png)

>>>>

![](figures/fig1.png)

@@

![](figures/fig2.png)

> __Fig 2. Comparison of alignment between AquaMaps and IUCN range data.__ (A) Distribution alignment (overlap of smaller range within larger) versus area ratio (the ratio of smaller range area to the larger range area) for `r format(n_spp_both, big.mark = ',')` species included in both IUCN and AquaMaps datasets.  The upper right quadrant comprises species whose maps largely agree in both spatial distribution and the extent of described ranges (n = `r n_q1`; `r round(n_q1/nrow(spp_list_quads) * 100, 1)` %).
The upper left quadrant comprises species whose maps agree well in distribution, but disagree in area
(n = `r n_q2`; `r round(n_q2/nrow(spp_list_quads) * 100, 1)` %).
The lower right quadrant includes species for which the paired maps generally agree in range area, but disagree on where those ranges occur
(n = `r n_q3`; `r round(n_q3/nrow(spp_list_quads) * 100, 1)` %).
The lower left quadrant indicates species for which the map pairs agree poorly in both area and distribution
(n = `r n_q4`; `r round(n_q4/nrow(spp_list_quads) * 100, 1)` %).
(B) Alignment quadrant breakdown of species by taxonomic group.

@@

![](figures/fig3.png)

@@

![](figures/fig4.png)

@@

![](figures/fig5.png)

### 2016-09-25 ms_4_refs.Rmd
cleaning up and preparing to make public for submit

<!-- Acknowledgments. List acknowledgments and funding sources. PNAS collaborates with FundRef to use a standard taxonomy of funder names. Dedications are rarely allowed. -->

@@

<!--
References. References must be in PNAS style. Only published or in-press papers and books may be cited in the reference list. For references to in-press articles, please confirm with the cited journal that the article is in press and include a DOI number and online publication date. Unpublished abstracts of papers presented at meetings or references to "data not shown" are not permitted. References should be cited in numerical order as they appear in text, and all references, including for the SI, should be included in the main manuscript file. Because tables and figures will be inserted in the text where first cited, references in these sections should be numbered accordingly. Include the full title for each cited article. All authors (unless there are more than five) should be named in the citation. If there are more than five, list the first author's name followed by et al. Provide inclusive page ranges for journal articles and book chapters. Cite databases in the text or as footnotes.

Journal articles are cited as follows:

10. Neuhaus J-M, Sitcher L, Meins F, Jr, Boller T (1991) A short C-terminal sequence is necessary and sufficient for the targeting of chitinases to the plant vacuole. Proc Natl Acad Sci USA 88(22):10362–10366.
-->

>>>>

@@

<!-- references will be automatically added from Zotero bib when knitting the document from manuscript-main.Rmd -->

### 2016-09-25 ms_5_figures.Rmd
cleaning up and preparing to make public for submit

![Taxonomic and geographic representation](figures/Fig_1.png)

@@

![Quadrant plot and spp breakdown by quadrant](figures/Fig_2.png)

@@

![coral area subject to depth clipping](figures/Fig_3.png)

@@

![aquamaps edge comparison](figures/Fig_4.png)

@@

![Change in MPA coverage](figures/Fig_5.png)

``` {r figure_legends, child = 'ms_5_fig_legends.Rmd', eval = FALSE}
```

>>>>

![Taxonomic and geographic representation](figures/fig1.png)

@@

![Quadrant plot and spp breakdown by quadrant](figures/fig2.png)

@@

![coral area subject to depth clipping](figures/fig3.png)

@@

![aquamaps edge comparison](figures/fig4.png)

@@

![Change in MPA coverage](figures/fig5.png)

### 2016-09-25 ms_6_supplemental.Rmd
cleaning up and preparing to make public for submit

---
title: "Supplemental Figures: Aligning marine species range data to better serve science and conservation"
author: "Casey O'Hara, Jamie C. Afflerbach, Courtney Scarborough, Benjamin S. Halpern"
output:
  word_document: default
  pdf_document:
    number_sections: no
    toc: no
  html_document:
    highlight: haddock
    number_sections: no
    theme: spacelab
    toc: no
---

<!--

-->

<!-- methods: -->
<!-- IUCN raw -> grid -> raster -> final -->
<!-- AM raw -> presence -->

<!-- results/discussion: -->
<!-- quad plot with risk and four species (?) -->
<!-- four representative maps -->

<!-- coral quadrant shifts -->

<!-- AM thresholds? not mentioned in body of paper as of yet -->

## Preparing AquaMaps and IUCN data layers

![](figures/Fig_S1.png)

> __Fig S1.  Examples of AquaMaps and IUCN raw species range data.__ (A, B) AquaMaps distribution of _Thunnus alalunga_ (Albacore Tuna) (AquaMaps 2013e) showing (A) global range with varying probabilities of occurrence assigned to 0.5° grid cells and (B) presence within 0.5° grid cells. (C, D) IUCN distribution of _T. alalunga_ (IUCN 2011b) represented as (C) extent of occurrence polygons and (D) presence within 0.5° grid cells.

@@

![](figures/Fig_S2.png)

> __Fig S2.  Rasterizing shapefiles provided by IUCN.__ A portion of the _T. alalunga_ range map is used to exemplify the rasterization process.  To enable direct comparison of IUCN species ranges to AquaMaps species ranges, the raw IUCN polygon (A) is overlaid with a 0.5° degree grid matching the AquaMaps grid (B).  Each cell is assigned a value of "present" if the cell overlaps any portion of the polygon (C).  The resulting raster (D).

## Representative maps from each quadrant

![](figures/Fig_S3.png)

> __Fig S3.  Representative species maps to illustrate each quadrant from Fig 2A.__ (AquaMaps 2013abcd; Conch 2013ab; IUCN 2011a; IUCN 2012) Each map is positioned to match its quadrant in Fig 2A.  FAO Major Fishing Area boundaries [@fao_fisheries_and_aquaculture_department_cwp_2015] are outlined in light grey.
(A) Distribution-matched: _Conus episcopatus_, the dignified cone snail.  Distributions show excellent overlap in the western Pacific, though IUCN range extends well beyond the bounds of the AquaMaps range.
(B) Well-matched: _Kajikia albida_, the Atlantic white marlin.  Distributions from each data set show nearly complete overlap, and very similar range size.
(C) Poorly-matched: _Acanthurus nigroris_, the blue-lined surgeonfish.  IUCN predicts species distribution only near the Hawaiian islands; AquaMaps predicts extensive distribution throughout the central and western Pacific Ocean.  The datasets align in neither distribution nor range size.
(D) Area-matched: _Conus magnificus_, the magnificent cone snail.  Distributions overlap in the southern Pacific, but align poorly elsewhere.  The range sizes are similar.

@@

## Shifts in coral species range map alignment due to depth clipping

![](figures/Fig_S4.png)

> __Fig. S4.  Shift in alignment of paired-map coral species due to clipping IUCN ranges to areas shallower than 200 m.__  The grey lines represent the change in apparent alignment for a single species.  Most coral species shift rightward from the upper left quadrant to the upper right, with little if any loss in distribution alignment, since in general, only unsuitable habitat has been removed.  Leftward shifts can be seen in species whose larger original range is represented in AquaMaps; by trimming IUCN ranges, the area ratio becomes smaller.

@@

Conch Books, Hackenheim, Germany 2013. Conus episcopatus. The IUCN Red List of Threatened Species. Version 2016-2

Conch Books, Hackenheim, Germany 2013. Conus magnificus. The IUCN Red List of Threatened Species. Version 2016-2

International Union for Conservation of Nature (IUCN) 2011. Kajikia albida. The IUCN Red List of Threatened Species. Version 2016-2

International Union for Conservation of Nature (IUCN) 2011. Thunnus alalunga. The IUCN Red List of Threatened Species. Version 2016-2

International Union for Conservation of Nature (IUCN) 2012. Acanthurus nigroris. The IUCN Red List of Threatened Species. Version 2016-2

www.aquamaps.org, version of Aug. 2013. Computer generated distribution maps for Conus episcopatus, with modelled year 2100 native range map based on IPCC A2 emissions scenario. Web. Accessed 11 Sep. 2016.

www.aquamaps.org, version of Aug. 2013. Computer generated distribution maps for Conus magnificus, with modelled year 2100 native range map based on IPCC A2 emissions scenario. Web. Accessed 11 Sep. 2016.

www.aquamaps.org, version of Aug. 2013. Computer generated distribution maps for Kajikia albida (Atlantic white marlin), with modelled year 2100 native range map based on IPCC A2 emissions scenario. Web. Accessed 11 Sep. 2016.

www.aquamaps.org, version of Aug. 2013. Reviewed distribution maps for Acanthurus nigroris (Bluelined surgeonfish), with modelled year 2100 native range map based on IPCC A2 emissions scenario. Web. Accessed 11 Sep. 2016.

www.aquamaps.org, version of Aug. 2013. Reviewed distribution maps for Thunnus alalunga (Albacore), with modelled year 2100 native range map based on IPCC A2 emissions scenario. Web. Accessed 11 Sep. 2016.

>>>>

---
title: "Supplemental Figures: Aligning marine species range data to better serve science and conservation"
output:
  word_document: default
  pdf_document:
    number_sections: no
    toc: no
  html_document:
    highlight: haddock
    number_sections: no
    theme: spacelab
    toc: no
---

## Supplemental figure captions

![](figures/S1_fig.png)

> __Fig S1. Examples of AquaMaps and IUCN raw species range data.__ (A, B) AquaMaps distribution of Thunnus alalunga (Albacore Tuna) [23] showing (A) global range with varying probabilities of occurrence assigned to 0.5° grid cells and (B) presence within 0.5° grid cells. (C, D) IUCN distribution of T. alalunga [24] represented as (C) extent of occurrence polygons and (D) presence within 0.5° grid cells.

@@

![](figures/S2_fig.png)

> __Fig S2. Rasterizing shapefiles provided by IUCN.__ A portion of the T. alalunga range map [24] is used to exemplify the rasterization process. To enable direct comparison of IUCN species ranges to AquaMaps species ranges, the raw IUCN polygon (A) is overlaid with a 0.5° degree grid matching the AquaMaps grid (B). Each cell is assigned a value of "present" if the cell overlaps any portion of the polygon (C). The resulting raster (D).

![](figures/S3_fig.png)

> __Fig S3. Representative species maps to illustrate each quadrant from Fig 2A.__ Each map is positioned to match its quadrant in Fig 2A. FAO Major Fishing Area boundaries [11] are outlined in light grey. (A) Distribution-aligned: Conus episcopatus, the dignified cone snail [25, 26]. Distributions show excellent overlap in the western Pacific, though IUCN range extends well beyond the bounds of the AquaMaps range. (B) Well-aligned: Kajikia albida, the Atlantic white marlin [27, 28]. Distributions from each data set show nearly complete overlap, and very similar range size. (C) Poorly aligned: Acanthurus nigroris, the blue-lined surgeonfish [29, 30]. IUCN predicts species distribution only near the Hawaiian islands; AquaMaps predicts extensive distribution throughout the central and western Pacific Ocean. The datasets align in neither distribution nor range size. (D) Area-aligned: Conus magnificus, the magnificent cone snail [31, 32]. Distributions overlap in the southern Pacific, but align poorly elsewhere. The range sizes are similar.

@@

![](figures/S4_fig.png)

> __Fig S4. Shift in alignment of paired-map coral species due to clipping IUCN ranges to areas shallower than 200 m.__ The grey lines represent the change in apparent alignment for a single species. Most coral species shift rightward from the upper left quadrant to the upper right, with little if any loss in distribution alignment, since in general, only unsuitable habitat has been removed. Leftward shifts can be seen in species whose larger original range is represented in AquaMaps; by trimming IUCN ranges, the area ratio becomes smaller.

@@

23. www.aquamaps.org, version of Aug. 2013. Reviewed distribution maps for Thunnus alalunga (Albacore), with modelled year 2100 native range map based on IPCC A2 emissions scenario. Web. Accessed 11 Sep. 2016.

24. International Union for Conservation of Nature (IUCN) 2011. Thunnus alalunga. The IUCN Red List of Threatened Species. Version 2016-2

25. www.aquamaps.org, version of Aug. 2013. Computer generated distribution maps for Conus episcopatus, with modelled year 2100 native range map based on IPCC A2 emissions scenario. Web. Accessed 11 Sep. 2016.

26. Conch Books, Hackenheim, Germany 2013. Conus episcopatus. The IUCN Red List of Threatened Species. Version 2016-2.

27. www.aquamaps.org, version of Aug. 2013. Computer generated distribution maps for Kajikia albida (Atlantic white marlin), with modelled year 2100 native range map based on IPCC A2 emissions scenario. Web. Accessed 11 Sep. 2016.

28. International Union for Conservation of Nature (IUCN) 2011. Kajikia albida. The IUCN Red List of Threatened Species. Version 2016-2.

29. www.aquamaps.org, version of Aug. 2013. Reviewed distribution maps for Acanthurus nigroris (Bluelined surgeonfish), with modelled year 2100 native range map based on IPCC A2 emissions scenario. Web. Accessed 11 Sep. 2016.

30. International Union for Conservation of Nature (IUCN) 2012. Acanthurus nigroris. The IUCN Red List of Threatened Species. Version 2016-2.

31. www.aquamaps.org, version of Aug. 2013. Computer generated distribution maps for Conus magnificus, with modelled year 2100 native range map based on IPCC A2 emissions scenario. Web. Accessed 11 Sep. 2016.

32. Conch Books, Hackenheim, Germany 2013. Conus magnificus. The IUCN Red List of Threatened Species. Version 2016-2.
